### 2011-01-26 paper/platformDetails.tex
Moved robot figure to intro
added information about motors, printing, length and weight

% Describe how you implemented your system and how you structured it. 
% This should give an overview of the system, not a detailed 
% documentation of the code. The documentation of the code is part of 
% the code you hand in. You might want to comment on high-level design 
% decisions that you made. Also explain how you obtained your
% data and any pre-processing you did to it.
\acmFig{robot_close.jpg}{1}{The robot}
\acmFig{topdown.png}{1}{A figure of the robot from a top-down perspective,
with motors labeled}

The quadruped robot (\figref{robot_close.jpg}) has an on-board computer running Linux. The lower
level drivers are in C and the system is implemented in
Python.

>>>>

% Describe how you implemented your system and how you structured it. 
% This should give an overview of the system, not a detailed 
% documentation of the code. The documentation of the code is part of 
% the code you hand in. You might want to comment on high-level design 
% decisions that you made. Also explain how you obtained your
% data and any pre-processing you did to it.

\acmFig{topdown.png}{1}{A figure of the robot from a top-down perspective,
with servos labeled}

The quadruped robot was printed on the Objet
Connex 500 3-D Printing System. It weights 1884 g and measures approximately
15 centimeters from leg to leg in the crouch position depicted in
\figref{robot_close.jpg}. There are a total of 9 AX-12+ Dynamixel
Servomotors: 4 outer leg joint
servos, 4 inner leg joint servos, and a final servo at the center "hip" of the
robot (displayed in \figref{topdown.png}). The robot has an on-board computer running Linux. 
The lower level drivers are in C and the system is implemented in Python.
